\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
     I would like to thank Professor Takashi Onaka firstly for guiding me since I first came to his laboratory as an undergraduate summer intern, in June 2012. I'm not sure if I've worked hard enough for the honor of being his last Ph.D. student, but its been a pleasure. I am extremely happy that I to complete my degree here. I wish him the happies of retirements, while sincerely doubting he will be able to stay away from research for long.

     Onaka-sensei and the members of the Onaka-lab have literally helped me to survive here, assisting any time that I have had difficulty adjusting as a foreign student.

    Itsuki Sakon has helped me greatly from the moment I arrived in Japan (literally.) It is also quite refreshing when his driving skills leave me at my destination much earlier than planned.

     I have been very lucky to have helpful co-authors for the various posters and abstracts I have presented in the course of this thesis: Ho-Gyu Lee, Daisuke Ishihara, Yasuo Doi, Ho-Gyu Lee, Mark Hammonds, Fumihiko Usui, Takafumi Ootsubo, Ryou Ohsawa, Tamami Okada, Hidehiro Kaneda --- especially, my international collaborators kind enough to host me over the years, Ronin Wu, Mridusmita Buragohain, Rupjyoti Gogoi, Frederic Galliano, Amit Pathak, Martin Giard, and Olivier Berne.

     My undergraduate advisor, Steven Gibson, deserves a special thanks for continued kind encouragement and research advice even now that I have graduated from WKU.

     Most personally, I must thank my mother, Catherine Marie Bell who has supported me more than seems possible for a single human being. The same goes to my younger siblings, Joseph, Emma, Caleb, and Noah who I have too few opportunities to help grow up. I thank also Deborah and Faithie (``Mama'') Guffy, who have been like aunt and gradnmother to us all.

     My day to day life in Japan has been brightened by partner of five years, Yuki Sugisawa \begin{CJK}{UTF8}{min}(杉澤友紀)\end{CJK}. His family too, who have been an unofficial host-family over the years, Chikako \begin{CJK}{UTF8}{min}(千賀子様),Hiromi (宏美様), Takeshi (剛様), and Chiri\end{CJK}. Even his grandmother Junko and grandfather Sadao Masuda \begin{CJK}{UTF8}{min}(桝田順子と定雄様)\end{CJK} have shown me much kindness during my visits to Osaka.

     A special note of thanks is owed to my friends who have inspired me and shared moral support, from back in the US, throughout my program: Alexandria Boswell, Hannah Kagan-Moore, Alexander Chen, George Johnson, Nicolas Tarantino, and John Max Wilson; as well as my classmates at U.Tokyo, Scarlet Elgueta, Jerome de Leon, Ryouta Kawamata, Takahiro Sudoh, Taku Okamura, John Livingston, Kyle Mede, Yuta Kato, and others.

     This project could not have found its way to any assemblance of completion without kind and insightful discussions with Nathalie Ysard, Alessandra Candian,  Chikako Yasui, Norita Kawanaka, Bruce Draine, Chris Tibbs, Francois Boulanger, Brandon Hensley, Clive Dickinson, Yasushi Suto, Othman Benomar, and Anthony Jones.

     The staff of GRID, Inc., especially Mehdi Shibahara and Ying-Ming Chen, helped guide my career choices and advance my knowledge of machine learning besides being the best lunch pals.

     I wish the best of luck to my kohais in Onaka-lab: Izumi Endo, Jin Zhang, Tomoyuki Kimura, Ayato Ikeuchi, and Mingie Jian in their continued studies and careers. I also want to express special thanks to the staff of the International Liaison Office, for advising me over the last five years, even since I was an undergraduate research internship student, in the UTRIP program of 2012.

     This project acknowledges a wide range of authors. I would like also to credit especially any of those whose names did not make it into the literature, for whatever reason. Especially the many women and minorities who have made direct or indirect contribtuions to science, but have been systematically overlooked and underrepresented in journals and awards.

     My financial support for living and tuition expenses during this time has been generously provided by "MEXT", the Ministry of Education, Culture, Sports, Science and Technology (\begin{CJK}{UTF8}{min}文部科学省.\end{CJK}). This research is based on observations with AKARI, a JAXA project with the participation of ESA; Planck (http://www.esa.int/Planck), an ESA science mission with instruments and contributions directly funded by ESA Member States, NASA, and Canada; and IRAS, a joint project of the US, UK and the Netherlands.

    This research made use of Montage. It is funded by the National Science Foundation under Grant Number ACI-1440620, and was previously funded by the National Aeronautics and Space Administration's Earth Science Technology Office, Computation Technologies Project, under Cooperative Agreement Number NCC5-626 between NASA and the California Institute of Technology
