\chapter{Summary}

\chapter{Discussion}
  \label{ch:discussion}

    We have compared AME with infrared dust emission from 2 approaches. The results and discussion contained here apply to an angular scale of approximately 1$^{\circ}$. In general, our results support an AME-from-dust hypothesis. We do not find evidence that the AME is exclusively carried by PAHs, but we do find evidence that the AME correlates with the AKARI 9 micron band emission better than other MIR bands- and better than all other IR bands sampled, when looking at the particularly prominent AME region, $\lambda$~Orionis. The results may be consistent with a scenario in which PAH mass, cold dust, and the AME are all tightly correlated.

\section{AME:$T$, $G_{0}$}

    According to spinning dust theory outlined in \cite{draine98a} and in subsequent works by \cite{ysard10a}, the AME profile and intensity will depend in part on the ISRF- but as is well-stated in \cite{hensley17a}, exactly how the ISRF will affect the AME SED is a more complicated question. Absorbed starlight photons may be able to rotationally excite the carriers, but if an enhanced ISRF leads to increased dust heating, then the increased IR emission can rotationally de-excite the carriers. However the ISRF affects not only the dust temperature but ionization of the carriers.


\section{Microwave foreground component separation}

    There are known degeneracies between the foreground parameters of the COMMANDER maps (spinning-dust, and free-free, synchrotron components as described in \cite{planck15X}.) This can be demonstrated by comparing the ratio map of the PCXV intensity to thermal dust intensity.


  From these results, we cannot confirm or rule out a spinning-PAH hypothesis on an all-sky, 1$^{\circ}$ scale. While nanosilicates or magentic dipole emission from dust may be plausible contributors to the AME, as shown in \cite{hoang16a, hensley17a}, we do not find (at least at resolutions considered here) that PAHs can be ruled-out as a carrier. While it is true that the FIR in our study has a tighter correlation with AME than PAH-related bands, the correlation with PAH emission remains. This is true both when considering AME intensity to Either this is a coincidental correlation- PAHs and AME are both correlated with the ``actual'' carrier/s of AME, MIR phometric bands are not as good of a tracer of the actual PAH mass as we believed, or perhaps that PAHs are indeed contributing to the AME but that they are just one of multiple sources of the AME.

   If it can be shown that IR emission from non-PAH small dust particles, such as nanosilicates strongly correlates with the AME, another very interesting question would need to be addressed: why does PAH emission \textit{not} show a strong correlation? Do PAHs not have the range of dipole moments needed to produce emission in the 10 - 90 GHz range? Because, as is described in \cite{draine98a} and again in \cite{hensley17b}, such small particles should be spinning at the frequencies consistent with AME. Thus if we believe a particular class of small dust particles to exist, PAHs, nanosilicates, or otherwise- then they must be producing microwave emission, unless they do not have a permanent electric dipole.

  If there is a sufficient abundance of PAHs with an electric dipole, then we must consider the possibility that the data currently available to do not offer the necessary spatial resolution, or that the photometric bands used do not allow us to adequately separate the individual dust components (i.e. the PAH features from potential nanosilicate features) and/or microwave foreground emission components (free-free from spinning-dust.) We look forward to continued environment-resolved comparisons to investigate the potential AME-PAH (or AME-nanosilicates, iron nanoparticles) relationship in a region by region, especially given the disagreement we find between our examination of lambda Orionis and the all-sky analysis.
